\section{The Research Proposal}
\subsection{Problem Definition and Solution Approach.}
The presence of the splitting in the lowest excitonic state is an unwanted effect in QDs that causes a degradation in the degree of entanglement between the two photons in the biexciton-exciton radiative cascade by lifting the degeneracy of the levels\cite{Winik2017}. This is due to several causes but mainly as a result of the asymmetry of the QD.$\newline$
Several methods were investigated to control the FFS, such as inducing strain and magnetic and electric fields, but the problem persists. A more straightforward approach is to assume that the FFS can not be eliminated completely and attempt to restore the entanglement after the photons emission. 
\subsection{Theoretical formulation (exciton).}
The state of a photon emitted from exciton excitation is described as:
\begin{equation}
	\ket{\Psi(t)} = \alpha\ket{H_X}\cdot e^{\frac{-iE_H t}{\hslash}}+\beta\ket{V_X}\cdot e^{\frac{-iE_Vt}{\hslash}}
\end{equation}
Here $E_{H,V}$ are the energy levels,$H_X$ and $V_X$ are the horizontal and vertical respectively, and $\alpha$,$\beta$ are coefficients such that $\alpha^2 +\beta^2 = 1$.This can be rewritten as:
  \begin{equation}
  	\ket{\Psi(t)} = \alpha\ket{H_X}+\beta\ket{V_X}\cdot e^{\frac{-i\triangle E t}{\hslash}}
  \end{equation}
Where $\triangle E = E_H -E_V$. This can be simplified by replacing $ \frac{\triangle E}{\hslash}$ with $\omega$:
\begin{equation}
	\ket{\Psi(t)} = \alpha\ket{H_X}+\beta\ket{V_X}\cdot e^{-i\omega t}
\end{equation}
\subsection{Theoretical formulation (biexciton-exciton)}
The state of the two photons emitted from the radiative cascade is described as follows:
	\begin{equation}
	\ket{\Psi(t)} = \alpha(\ket{H_{XX} \otimes  H_X}\cdot e^{\frac{-iE_H t}{\hslash}}+\ket{V_{XX}\otimes V_X}\cdot e^{\frac{-iE_Vt}{\hslash}})
	\end{equation}
 Where $HH_X$ and $HH_V$ are the horizontal and vertical polarization of the biexciton, $\alpha$ is a global phase. Same with the exciton, we can simplify the function to:
\begin{equation}
	\ket{\Psi(t)} = \alpha(\ket{H_{XX} \otimes H_X}+\ket{V_{XX}\otimes V_X}\cdot e^{-i\omega t})
\end{equation}
\subsection{Rotation of the exciton's polarization.}
If we construct a device that allows us to induce a time-dependent phase shift to the exciton polarization, then we can write phase relations as:
\begin{equation} \label{exciton_phases}
\begin{aligned} 
        &\Phi_{H_{X}}{(t,t_{prop})} = K_{H_{X}}\cdot(t-t_{prop}) + \Phi^0_{H_{X}} &\\
		&\Phi_{V_{X}}{(t,t_{prop})} = K_{V_{X}}\cdot(t-t_{prop}) + \Phi^0_{V_{X}} 
\end{aligned}
\end{equation}
Here the  K's are the different slopes that introduce the shift to the photons' polarizations, and  $\Phi^0$'s are the initial phase of the photons. $t_{prop}$ is the propagation times of the photons from the quantum dot to the device. Since it's constant time, we can simplify the function by including it in the constant phase $\Phi^0$.
\begin{equation}
\begin{split}
		\ket{\Psi(t)}= \alpha( \ket{H_{X}}\cdot e^{i\Phi_{H_{X}}(t_{X}-t^{x}_{start})})+
		\beta (\ket{V_{X}}\cdot e^{i\Phi_{V_{X}}(t_{X}-t^{x}_{start})}\cdot e^{-i\omega t})
  \end{split}
\end{equation} 
Where $t_x$ is the random emission time of the exciton photon, and $t_{start}$ is the time when ramping of the differential phase begins. Substituting relations (\ref{exciton_phases}) and reorganizing the terms, we get:
\begin{equation}
	\ket{\Psi(t)} = \alpha\ket{H_X}+\beta\ket{V_X}\cdot e^{i\Phi}
\end{equation}
where $\Phi(t)$ :
\begin{equation}
\begin{split}  
\begin{aligned} 
	\Phi(t) = &(K_{V_X}-K_{H_X} + \omega)\cdot t_x -\\
 &t^X_{Start} \cdot(K_{V_X}-K_{H_X})+\\
 &(\Phi^0_{V_{X}}-\Phi^0_{H_{X}})
 \end{aligned}
 \end{split}
\end{equation}
For the function to be independent of the time $t_x$, the following condition must be met:
\begin{equation}
K_{V_X}-K_{H_X} =-\omega 
\end{equation}
Since we are interested only in the relative phase, we can further reduce the condition by introducing phase shift to only one direction:
\begin{equation}
K_{V_X} =-\omega 
\end{equation}
\subsection{Restoring the entanglement of the photons in the biexciton-exciton radiative cascade.}

Similar to the treatment of the exciton treatment, We can construct two devices that allow us to induce phase shift to both the biexciton and exciton polarizations, The time-dependent phase relations to both photons are: 
\begin{equation} \label{biexciton_phases}
\begin{aligned} 
		&\Phi_{H_{XX}}{(t,t_{prop})} = K_{H_{XX}}\cdot(t-t_{prop}) + \Phi^0_{H_{XX}} & \\	&\Phi_{V_{XX}}{(t,t_{prop})} = K_{V_{XX}}\cdot(t-t_{prop}) + \Phi^0_{V_{XX}} \\
        &\Phi_{H_{X}}{(t,t_{prop})} = K_{H_{X}}\cdot(t-t_{prop}) + \Phi^0_{H_{X}} &\\
		&\Phi_{V_{X}}{(t,t_{prop})} = K_{V_{X}}\cdot(t-t_{prop}) + \Phi^0_{V_{X}} 
\end{aligned}
\end{equation}
Here the K's are the different slopes that introduce the shift to the photons' polarizations, and  $\Phi^0$'s are the initial phase of the photons. $t_{prop}$ is the propagation times of the photons from the quantum dot to the device. Since it's constant time, we can simplify the function by including it in the constant phase $\Phi^0$.
By taking the starting time of our system as the biexciton excitation time, we can write the state using the $t_x$ and $t_{xx}$ ( where $t_{xx}$ and $t_{x}$ are the random emission times of the biexciton and exciton respectively), as follows:
\begin{equation}
\begin{split}
		\ket{\Psi(t)}= \alpha(\ket{H_{XX}}\cdot e^{i\Phi_{H_{XX}}(t_{XX}-t^{xx}_{start})} \otimes 
		\ket{H_{X}}\cdot e^{i\Phi_{H_{X}}(t_{XX}+t_{X}-t^{x}_{start})}+\\
        \ket{V_{XX}}\cdot e^{i\Phi_{V_{XX}}(t_{XX}-t^{xx}_{start})} \otimes 
		\ket{V_{X}}\cdot e^{i\Phi_{V_{X}}(t_{XX}+t_{X}-t^{x}_{start})}\cdot e^{-i\omega t})	
  \end{split}
\end{equation} 
Substituting relations (\ref{biexciton_phases}) and reorganizing the terms, we get:
\begin{equation}
	\Psi(t) = \ket{H_{xx}H_x}+e^{i\Phi}\ket{V_{xx}V_x}
\end{equation}
where $\Phi(t)$ :
\begin{equation}
\begin{split}  
\begin{aligned} 
	\Phi(t) = &(K_{V_{XX}}-K_{H_{XX}}+K_{V_X} - K_{H_X})\cdot t_{xx}+(K_{V_X}-K_{H_X} + \omega)\cdot t_x -\\
 &t^{XX}_{Start} \cdot(K_{V_{XX}} - K_{H_{XX}})-t^X_{Start} \cdot(K_{V_X}-K_{H_X})+\\
 &(\Phi^0_{V_{XX}}-\Phi^0_{H_{XX}}+\Phi^0_{V_{X}}-\Phi^0_{H_{X}})
 \end{aligned}
 \end{split}
\end{equation}
For the function to be independent of the times $t_{xx}$ and $t_{x}$, the following condition must be met:
\begin{equation}
	K_{V_X}-K_{H_X} = -\omega
\end{equation}
\begin{equation}
	(K_{V_{XX}} -K_{H_{XX}}) = -(K_{V_X}-K_{H_X})
\end{equation}
The same with the exciton rotation treatment, We can further simplify the conditions by inducing a shift in one direction:
\begin{equation}
	K_{V_X} = -\omega
\end{equation}
\begin{equation}
	K_{V_{XX}} = -K_{V_X}
\end{equation}
\subsection{Additional proposed advances}
\subsubsection{Combining the radiative cascade into the knitting machine.}
\textcolor{red} {I'm not sure about the subject; requires more discussion. }
\subsubsection{Using the experimental system for feed-forward operations in 1D cluster states.}
I propose using our constructed device to perform feed-forward operations by rerouting each photon based on information gained about the previous photon in the cluster state. 